% multiple1902 <multiple1902@gmail.com>
% bachelor.tex
% Copyright 2011~2012, multiple1902 (Weisi Dai)
% https://code.google.com/p/xjtuthesis/
% 
% It is strongly recommended that you read documentations located at
%   http://code.google.com/p/xjtuthesis/wiki/Landing?tm=6
% in advance of your compilation if you have not read them before.
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License, either version 1.3
% of this license or (at your option) any later version.
% The latest version of this license is in
%   http://www.latex-project.org/lppl.txt
% and version 1.3 or later is part of all distributions of LaTeX
% version 2005/12/01 or later.
%
% This work has the LPPL maintenance status `maintained'.
% 
% The Current Maintainer of this work is Weisi Dai.
%
\documentclass[
    bachelor, 
    %bigskip, % sets linespread factor to 1.5
    truefont, % just turn it on when using Windows
    %nofont, % remember to manally set the fonts
    pdflinks,
    %colorlinks,
    %compact,
    ]{xjtuthesis}

% Compact is enabled so that blank page VI does not appear

\graphicspath{{figures/}}

\begin{document}
\input{meta.tex}
\xjtucinfopage
\xjtueinfopage
\xjtutoc
\clearpage

\xjtucontent
\input{pages/preface.tex}
\input{pages/relatedtech.tex}
\input{pages/analysis.tex}
\input{pages/design.tex}
\input{pages/implementation.tex}
\input{pages/evaluation.tex}
\input{pages/conclusion.tex}

\xjtuendcontent

\xjtubib{bibliography.bib}

\xjtuappendix
\input{pages/appendice.tex}
\xjtuendappendix

\xjtuspchapter{致谢}{致\qquad 谢}
\par
首先感谢我的指导老师，西安交通大学的安健老师，美国加州大学洛杉矶分校的Prof. Jeff Burke和Prof. Lixia Zhang的耐心指导。
\par
感谢西安交通大学和加州大学洛杉矶分校为我提供的机会。
\par
感谢父母对我的支持。
\par
感谢电信硕01班班主任朱正东老师、刘纯亮老师和各位同学对我的帮助。
\par
感谢Xingyu，Zening，Jeff. T，Alex，Anmol，Daisuke，Cole，Zoe等UCLA的同事、同学对我工作的兴趣，提供的支持和帮助。
\par
感谢Panasonic的Muramoto先生和西北大学的Xiaojiang Chen教授对我工作表示的浓厚兴趣。
\par
感谢XJTUThesis项目，特别感谢戴唯思同学提供\LaTeX模板。

\end{document}

